PANCHANGE_descriptives

### 2020-09-18 PANCHANGE_exclusion_descriptives.Rmd
updated the exclusion chunk in the exclusion_descriptives script

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds")) # NEEDS CHANGING TO THE DATA SET THAT COMES OUT OF THE VARIABLE CREATION
dim(dat.raw)
colnames(dat.raw)
```

@@

Exclude GLAD/EDGI individuals that didn't take part in COPING
Exclude individuals with NA for the MHD categories
Individuals with NAs for age/gender have already been excluded in pre-processing script.

```{r exclusion criteria for diagnoses analysis}
dat <- dat.raw %>%
  filter(
    !is.na(depressive_disorders) &
      !is.na(eating_disorders) &
      !is.na(psychotic_disorders) &
      !is.na(obsessive_compulsive_disorders) &
      !is.na(autism_spectrum_disorder) &
      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
      !is.na(control)
  ) %>% 
  drop_na(startDate.coping)

>>>>

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds"))
dim(dat.raw)
colnames(dat.raw)
```

@@

Exclude GLAD/EDGI individuals that didn't take part in COPING
Exclude individuals with NA for the MHD categories
Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be save and to double check previous programming.

"anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"

```{r}
             anxiety_disorders_numeric = "Anxiety disorders",
             depressive_disorders_numeric = "Depressive disorders",
             eating_disorders_numeric = "Eating disorders",
             obsessive_compulsive_disorders_numeric = "OCDs",
             psychotic_disorders_numeric = "Psychotic disorders",
             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
             autism_spectrum_disorder_numeric = "Autism",
             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
             mhd.personality_disorder_numeric = "Personality disorders",
             control_numeric = "Controls"
```

```{r Exclusion criteria for PANCHANGE}
dat <- dat.raw %>%
  filter( # Participants should have responded to the mental health diagnosis (MHD) questionnaire
  !is.na(depressive_disorders) &
 !is.na(anxiety_disorders) &
  !is.na(eating_disorders) &
  !is.na(obsessive_compulsive_disorders) &
 !is.na(psychotic_disorders) &
  !is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
  !is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
  !is.na(autism_spectrum_disorder) &
  !is.na(mhd.attention_deficit_hyperactivity_disorder) &
  !is.na(mhd.personality_disorder) &
  !is.na(control)
  ) %>% 
 filter(
   !is.na(data_group_gad) & # Participants should have answered at least the GAD, the PHQ, or the PCL once
   !is.na(data_group_phq) &
   !is.na(data_group_pcl)
 ) %>%
  drop_na(startDate.coping) %>% # Participant has answered the COPING/RAMP baseline questionnaire
  drop_na(Gender_collapsed) %>% # Participant has self-reported their gender
  drop_na(age_category_collapsed) # Participant has self-reported their age
